Data migration under a Changing Schema

### 2023-02-12 2022 Migration/articleMigration.tex
wip

\begin{abstract}
   To support incremental software development with a software generator bears the potential of decreasing the time to deploy changes.
   However, an increment that changes the database schema causes a nontrivial data migration problem.
   The problem is how to preserve the semantics of the data as much as possible and satisfy elementary business requirements at the same time.

>>>>

\begin{abstract}
   To support incremental software development with a software generator bears the potential of saving work and decreasing the time to deploy changes.
   However, increments that change the database schema cause nontrivial data migration issues.
   The problem is how to preserve the semantics of the data as much as possible and satisfy elementary business requirements at the same time.
